Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
Removed NOT COMPLETE from my sections

\textbf{A. OpenALPR}
{\color{red}\textbf{NOT COMPLETE}}
As stated in Section 3.4.1, OpenALPR is built on top of OpenCV, a computer vision library, and Tesseract OCR, an OCR engine. Tesseract OCR had additional dependencies that needed to be installed before it would compile.

@@

\textbf{B. Intrada ALPR}
{\color{red}\textbf{NOT COMPLETE}}
Intrada ALPR uses the SOAP protocol for exchanging information. To create SOAP requests, we used the \verb+SoapClient+ class available in PHP to create, send, and receive the output of our request.

>>>>

\textbf{A. OpenALPR}
As stated in Section 3.4.1, OpenALPR is built on top of OpenCV, a computer vision library, and Tesseract OCR, an OCR engine. Tesseract OCR had additional dependencies that needed to be installed before it would compile.

@@

\textbf{B. Intrada ALPR}
Intrada ALPR uses the SOAP protocol for exchanging information. To create SOAP requests, we used the \verb+SoapClient+ class available in PHP to create, send, and receive the output of our request.
